---
title: "Analyses experiment 1 - project CC"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(purrr)
library(afex)
library(papaja)
source('../../scripts/functions/plot_functions.R')
source('../../scripts/functions/analysis_functions.R')
```

## Load judgements data

Load data of the predictive judgements made during the learning trials. The CSV contains the following columns:


- **participant**: ID of the participant
- **group**: ID of the group (1: Counterconditioning -CC-, 2: Novelty-facilitated extinction -NFE-. 3: Standard extinction -SE-)
- **groupType**: Name of the group
- **phase**: Phase in which the trial took place
- **CS**: CS A or CS B
- **trial**: number of trial for that CS in that phase
- **soundType**: Sound presented as EI on that trial (positive, negative, neutral)
- **response**: Value of the predictive judgement provided on that trial (0-100)
- **rt**: Reaction time of the judgement (s)

```{r}
judgement_data <- read_csv('../data/judgement_data.csv')
```
Check that the data has been loaded correctly
```{r}
head(judgement_data)
```

Show the relationship between group code and group name and show how many participants per group were collected.
```{r}
judgement_data %>%
  n_participants()
```

\newpage
Types of trial per group and phase
````{r}
judgement_data %>%
  group_by (groupType, phase, CS, soundType, participant) %>%
  count() %>%
  group_by(CS, phase, groupType, soundType) %>%
  summarise(mean = mean(n))
```


## Filter data with the preregistered criteria:

- 1st criterion: mean of CS A trials 5 to 8 of acquisition phase equal or greater than 70
- 2nd criterion: mean of CS B trials 5 to 8 of acquisition phase equal or lower than 15
- 3rd criterion: mean of CS A trials 21 to 24 of treatment phase equal or lower than 25
- 4th criterion: mean of CS B trials 21 to 24 of treatment phase equal or lower than 15

```{r}
  judgement_data_filtered <- filter_all_criteria(judgement_data)
```

Participants per group after the filters
```{r}
judgement_data_filtered %>%
  n_participants()
```

\newpage

## Analysis and plots of judgements

### Summary graph and omnibus ANOVA for each phase
```{r, message=FALSE, fig.cap=c("**Figure 1.** Mean judgements during acqusition phase. Error bars indicate the standard error of the mean.", "**Figure 2.** Mean judgements during treatment phase. Error bars indicate the standard error of the mean.", "**Figure 3.** Mean judgements during test phase. Error bars indicate the standard error of the mean.")}
for (cur_phase in unique(judgement_data_filtered$phase)){
  judgement_data_filtered %>%
    plot_phase(cur_phase)
  cat('\n\n')
  judgement_data_filtered %>%
    omnibus_phase(cur_phase)
}
```

### Graph and preplanned t-tests in the first trial of the test phase for CS A
```{r, message=FALSE, fig.cap="**Figure 4.** Mean judgements during first trial of the test phase. Error bars indicate the standard error of the mean."}
plot_T1_ext(judgement_data_filtered)
```

```{r, results = 'hide'}
t.test_T1 (judgement_data_filtered,
  group_pairs = list(c("CC","NFE"), c("CC","SE"), c("NFE","SE")))
```

`r t.test_T1 (judgement_data_filtered,
             group_pairs = list(c("CC","NFE"), c("CC","SE"), c("NFE","SE")))`

\newpage
***

## Analysis and plots of ratings

### Load the ratings data and filter them keeping the same participants

Load data of the ratings of the CS made after each phase and of the sounds made at the end. The CSV contains the following columns:


- **participant**: ID of the participant
- **group**: ID of the group (1: Counterconditioning -CC-, 2: Novelty-facilitated extinction -NFE-. 3: Standard extinction -SE-)
- **groupType**: Name of the group
- **phase**: Phase in which the rating took place
- **type**: type of rating requested (Evaluation: Like/Dislike rating, Anxiety: Level of anxiety)
- **CS**: CS A or CS B
- **sound**: Sound presented as EI on that trial (positive, negative, neutral)
- **response**: Value of the rating provided (0-10) As values increase, the likeability is higher (Evaluation trials) or the anxiety is reduced (Anxiety trials).
- **rt**: Reaction time of the judgement (s)
```{r, message = FALSE}
evaluation_data_filtered <- read_csv('../data/evaluation_data.csv')
evaluation_data_filtered <- evaluation_data_filtered %>%
  filter(participant %in% as.integer(judgement_data_filtered$participant %>% unique()))
```

```{r, message = FALSE, fig.cap="**Figure 5.** Mean like/dislike ratings for each CS after each phase. Error bars indicate the standard error of the mean."}
plot_CS_evaluations (evaluation_data_filtered)
omnibus_phase_evaluations_CS (evaluation_data_filtered, "Ext")
```


```{r, results = 'hide'}
t.test_Ext_evaluations(evaluation_data_filtered)
```


`r t.test_Ext_evaluations(evaluation_data_filtered)`


```{r, message = FALSE, fig.cap = "**Figure 6.** Mean like/dislike ratings for each sound. Error bars indicate the standard error of the mean."}
plot_sound_evaluations(evaluation_data_filtered)
omnibus_phase_evaluations_sounds (evaluation_data_filtered, "Final")
```

