---
title: "Analyses experiment 1 - project CC"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r, message=FALSE}
library(tidyverse)
library(afex)
source('../../scripts/functions/plot_functions.R')
source('../../scripts/functions/analysis_functions.R')
# Colour-blind palette from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

## Load data

Load data of the predicitve judgements made during the learning trials. The CSV contains the following columns:


- **participant**: ID of the participant
- **group**: ID of the group (1: Counterconditioning -CC-, 2: Novelty-facilitated extinction -NFE-. 3: Standard extinction -SE-)
- **groupType**: Name of the group
- **phase**: Phase in which the trial took place
- **CS**: CS A or CS B
- **trial**: number of trial for that CS in that phase
- **soundType**: Sound presented as EI on that trial (positive, negative, neutral)
- **response**: Value of the predictive judgement provided on that trial (0-100)
- **rt**: Reaction time of the judgement (s)

```{r}
judgement_data <- read_csv('../data/judgement_data.csv')
```
Check that the data has been loaded correctly
```{r}
head(judgement_data)
```

Show the relationship between group code and group name and show how many participants per group were collected.
```{r}
judgement_data %>%
  n_participants()
```

Types of trial per group and phase
````{r}
judgement_data %>%
  group_by (groupType, phase, CS, soundType, participant) %>%
  count() %>%
  group_by(CS, phase, groupType, soundType) %>%
  summarise(mean = mean(n))
```


## Filter data with the preregistered criteria:

- 1st criterion: mean of CS A trials 5 to 8 of acquisition phase equal or greater than 70
- 2nd criterion: mean of CS B trials 5 to 8 of acquisition phase equal or lower than 15
- 3rd criterion: mean of CS A trials 21 to 24 of treatment phase equal or lower than 25
- 4th criterion: mean of CS B trials 21 to 24 of treatment phase equal or lower than 15

```{r}
  judgement_data_filtered <- filter_all_criteria(judgement_data)
```

Participants per group after the filters
```{r}
judgement_data_filtered %>%
  n_participants()
```

## Analysis and plots of judgements

### Summary graph and omnibus ANOVA for each phase
```{r, message=FALSE}
for (cur_phase in unique(judgement_data_filtered$phase)){
  judgement_data_filtered %>% 
    plot_phase(cur_phase, save = TRUE)
  judgement_data_filtered %>% 
    omnibus_phase(cur_phase)
}
```

### Graph and preplanned t-test in the first and second trial of the test phase for CS A
```{r}
  plot_T1T2_ext(judgement_data_filtered, save = TRUE)
  t.test_T1T2 (judgement_data_filtered,
               group_pairs = list(c("CC","NFE"), c("CC","SE"), c("NFE","SE")))
```

## Analysis and plots of ratings

### Load the ratings data and filter them keeping the same participants

```{r, message = FALSE}
evaluation_data_filtered <- read_csv('../data/evaluation_data.csv')
evaluation_data_filtered <- evaluation_data_filtered %>%
  filter(participant %in% as.integer(judgement_data_filtered$participant %>% unique()))
```

```{r}
plot_CS_evaluations (evaluation_data_filtered)
omnibus_phase_evaluations_CS (evaluation_data_filtered, "Ext")
t.test_Ext_evaluations(evaluation_data_filtered)
```

```{r}
plot_sound_evaluations(evaluation_data_filtered)
omnibus_phase_evaluations_sounds (evaluation_data_filtered, "Final")
```

